Does It Scale? Static Output Approximation of PHP Web Applications Using Symbolic Execution

### 2017-01-05 paper.tex
added code example for sec 2, maybe simplify

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{paralist}
\usepackage{listings}
\usepackage{lipsum}
\usepackage{cite}
\usepackage{enumerate}
\usepackage{subcaption}
\usepackage{cleveref}
\usepackage{ucs}
\usepackage{framed}

@@

\lstset{
language=PHP,
basicstyle=\ttfamily\tiny,
basewidth={0.5em,0.4em}, % for other columns settings
%columns=fullflexible,
numbers=left,
numberstyle=\tiny,
frame=single,
showstringspaces=false,
xleftmargin=2em,
framexleftmargin=1.5em
}

@@

% Workflow Graphic
\begin{figure*}[t!]
	\centerline{
	\includegraphics[width=0.95\textwidth]{images-paper/workflow}
	}
	\vspace{2mm}
	\caption{
		Overview of the workflow for tools based on static output approximation for dynamic web applications.	
	}
	\label{fig:approach}
\end{figure*}

>>>>

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{paralist}
\usepackage{listings,multicol}
\usepackage{lipsum}
\usepackage{cite}
\usepackage{enumerate}
\usepackage{subcaption}
\usepackage{cleveref}
\usepackage{ucs}
\usepackage{framed}

@@

\lstset{
	language=PHP,
	basicstyle=\ttfamily\tiny,
	basewidth={0.5em,0.4em}, % for other columns settings
	columns=fullflexible,
	numbers=left,
	numberstyle=\tiny,
	frame=single,
	showstringspaces=false,
	xleftmargin=2em,
	framexleftmargin=1.5em,
}

\newcommand{\dollar}{\mbox{\textdollar}}

@@

\begin{figure*}
	\centering
	\begin{subfigure}[center]{0.49\textwidth}%%[multicols=1]
\begin{lstlisting}
<form>
  <input type="text" name="name">
  <input type="submit" value="Submit">
</form>

<?php
  function titles($arg, $n) {
    $is = array(1,2,3);
    while ($n < shuffle($is)) {
      echo "<h1>" . $arg . "</h1><br>";
      $n += 1;
    }
  }

  call_user_func("title", "Headline", 4);

  $name = $_POST['name'];
  if (!isset($name)) {
    echo "No name entered!";
  } else {
    echo "Entered ". $name ."!";
  }
?>
\end{lstlisting}
		\caption{Snippet of server-side web application code}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[center]{0.49\textwidth}
\begin{lstlisting}[mathescape]
<form>
  <input type="text" name="name">
  <input type="submit" value="Submit">
</form>

// #repeat n < shuffle(is)
  <h1>Headline</h1>
// #endrepeat

// #if !isset(name)
  No name entered!
// #else
  Entered $\alpha$!
// #endif

\end{lstlisting}
		\caption{Symbolic output approximation}
    \end{subfigure}
    \vspace{2mm}
    \caption{Illustration of static ouptut approximation using symbolic
    execution}
\end{figure*}

% Workflow Graphic
%\begin{figure*}[t!]
%	\centerline{
%	\includegraphics[width=0.95\textwidth]{images-paper/workflow}
%	}
%	\vspace{2mm}
%	\caption{
%		Overview of the workflow for tools based on static output approximation for
%		% dynamic web applications.
%	}
%	\label{fig:approach}
%\end{figure*}
